Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ {\smaller \textbf{Final Draft - UNDER REVIEW}}

### 2015-05-13 Paper.tex
typo
fix block reward calculation
style
take the BLOCKHASH random number strategy into account

\subsection{Random Numbers}
Providing random numbers within a deterministic system is, naturally, an impossible task. However, we can approximate with pseudo-random numbers by utilising data which is generally unknowable at the time of transacting. Such data might include the block's hash, the block's timestamp and the block's coinbase address. For a series of such numbers, a trivial solution would be to work from the previous pseudo-random number, adding some constant amount and hashing the result.

This strategy does have a downside: a miner with sufficient power could alter any of the above values in order to deliver a seed in order to alter the outcome of the pseudorandom-based executions. For a more secure pseudo-random offering, all involved parties could agree on a number of data feed contracts; these could be combined along with the block timestamp and hashed to produce the first number in the series. By spreading the inputs and thus the trust between numerous parties the likelihood of a malicious miner altering the outcome becomes increasingly less likely.

>>>>

\subsection{Random Numbers}
Providing random numbers within a deterministic system is, naturally, an impossible task. However, we can approximate with pseudo-random numbers by utilising data which is generally unknowable at the time of transacting. Such data might include the block's hash, the block's timestamp and the block's coinbase address. In order to make it hard for malicious miner to control those values, one should use the {\small BLOCKHASH} operation in order to use hashes of the previous 256 blocks as pseudo-random numbers. For a series of such numbers, a trivial solution would be to add some constant amount and hashing the result.
